%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Nader AbdalGhani}
\address{Cairo, Egypt \linebreak +2(010) 017-96904}
\contacts{github.com/naderabdalghani \linebreak naderabdalghani@outlook.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Giza, Egypt}{Cairo University}{September 2016 — July 2021}
			\begin{itemize}
				\item B.Sc. in Computer Engineering.
				\item Relevant Coursework: Data Structures \& Algorithms, Object-Oriented Programming, Operating Systems, Software Engineering, Computer Architecture, Computer Networks, Database Systems, Machine Intelligence, Big Data Analytics.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{project rev}: Researched, mapped out and led the architecture and development of a 5-module audio-interactive personalizable chatbot. [Python, PyTorch, Hugging Face, Flask, Natural Language Processing (NLP)]
				\item \textbf{Nabd}: Incorporated internationalization, GPS tracking, and designed most of the user interface (UI) scenes and forms, contributing to the app becoming a \$60,000 government award finalist. [JavaScript, React Native, Redux]
				\item \textbf{E7gzly API}: Created, designed and documented a RESTful API featuring 17 endpoints for a football matches ticket reservation web app. [Python, Django, Graph Database Systems]
				\item \textbf{Othello (Reversi)}: Created a basic Othello game implementation that supports two types of playing agents: a human or a general minimax alpha-beta pruning agent. [Python, Artificial Intelligence (AI)]
				\item \textbf{Doclense}: Contributed to the development of an OCR web app by implementing a text separation algorithm and creating a classifier model achieving 99\% accuracy on a custom dataset. [Python, Image Processing, Neural Networks]
				\item \textbf{Database Tuning}: Reduced queries running time by an average of 60\% by utilizing memory management, indexes tuning, and query execution plan optimization. [Database Systems, Microsoft SQL Server]
				\item \textbf{kabsa}: Built a compiler using Bison \& Flex C++ interfaces that supports 8 language constructs, semantic and syntactic error detection and generates code for a hypothetical stack-based machine. [C++, Lex, Yacc, Compilers]
				\item \textbf{Battleships Game}: Developed the famous battleships guessing game, specifically the ships-placement mechanism and simulated scrolling chat using queues data structure and 8086 Assembly graphics mode. [8086 Assembly]
				\item \textbf{32-bit RISC Pipelined Processor}: Implemented a regex-based assembler and modelled the memory stage of a 5-stage 32-bit pipelined processor. [Python, VHDL]
				\item \textbf{Developed Dynamic Multilevel Feedback Queue Scheduling Algorithm with Aging Criteria for Starvation Mitigation}. [Research Paper]
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Work Experience}
		\begin{cvsubsection}{Freelance Software Developer}{}{May 2019 — Present}
			\begin{itemize}
				\item Sustained 100\% Job Success and Client Recommendation scores on Upwork.
				\item Implemented a financial analysis system using Google Apps Script API for a large-scale content publisher. Extensively optimized the system to run as quickly as possible under Google Sheets limitations.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Extracurricular Activities and Coursework}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Coursera Natural Language Processing Specialization.} [November 2020]
				\item \textbf{Udacity Deep Learning Nanodegree.} [September 2020]
				\item \textbf{CMP 2021 Conference Co-host:} Co-hosted and introduced teams in a 14-team conference.
				\item \textbf{1 Million Arab Coders Initiative Android Developer Track.} [April 2018]
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Skills}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{Programming Languages:} Python, C/C++, JavaScript, Java (familiar), SQL.
				\item \textbf{Frameworks:} PyTorch, Django, Flask, React Native, Hugging Face.
				\item \textbf{Tools:} Git \& GitHub, Google Cloud Platform, Microsoft SQL Server, Visual Studio, VS Code, PyCharm.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
